---
title: "DV_RProject 1"
output: html_document
---

**Members:** Andrea Curo, Dora Cheng, Sonam Shah

###Creating Multiple Graph Plots in R
1. Create an RStudio project
2. Pull data from oracle database cloud
3. Process with ggplot and order based on the desired category with facet wrap

```{r fig.width=10, fig.height=10}
source("../01 Data/df_selectorders.R", echo= TRUE)
```

Pulling the customer table information to plot how many customers are from each state.
```{r fig.width=10, fig.height=10}
source("../01 Data/df_selectcustomers_plot.R", echo= TRUE)
```

Pulling customers details table information to plot how many times an item was ordered.
```{r fig.width=10, fig.height=10}
source("../01 Data/df_selectdetails_plot.R", echo= TRUE)
```

Pulling items table information to plot how much each item cost.
```{r fig.width=10, fig.height=10}
source("../01 Data/df_selectitems_plot.R", echo= TRUE)
```

Pulling items table information to plot how long it took between when a customer ordered an item and it got shipped.
```{r fig.width=10, fig.height=10}
source("../01 Data/df_selectorders_plot.R", echo= TRUE)
```